Analysis_manuscript_mash_GxE

### 2020-10-29 R/Analysis_manuscript_mash_GxE.Rmd
Start manuscript 0.5 incorporating TEJ changes and genetic covariances

# View single trait mash outputs
```{r}
i=1 # site
j=1 # phe
k=1 # subpop: G&M, M, Gulf
suffix <- paste0("single_phe_", names(subpop_v)[k], "_", phe_single[j])

@@

Keep covariance matrices with point mass > 0.05 and add them to U_hyp

>>>>

# View single trait mash outputs
```{r}
i=1 # site
j=7 # phe
k=1 # subpop: G&M, M, Gulf
suffix <- paste0("single_phe_", names(subpop_v)[k], "_", phe_single[j])

@@

Keep covariance matrices with point mass > 0.05 and add them to U_hyp.
Add them as single effects (the remaining phe are 0)
And add them as combinations if possible.

Need to figure out what order the traits are in, after I set up Shat and Bhat matrices for mash. Maybe do this for GR50 first. Only two phenotypes instead of five.

1. Make mash inputs for five & two phenotypes for eight sites. Standardize phenotypes and clump SNPs.
2. Find trait order.  The trait order is the same order as the 'phenotypes' vector.
3. Make U_hyp in trait order.
4. Run mash with U_hyp.

```{r}
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
outputdir <- file.path(workingdir, "analysis", "gwas", "BLUPs", "single_sites")
site_v <- list(TX1 = "TX1", TX2 = "TX2", TX3 = "TX3", OK = "OK", MO = "MO",
               NE = "NE", MI = "MI", SD = "SD")#, eight_sites = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD"), tx_sites = c("TX1", "TX2", "TX3"), north_sites = c("MO", "NE", "MI", "SD"))
subpop_v <- list(Gulf_and_Midwest = "363g_12.1M", Midwest = "134g_8.8M", Gulf = "229g_10.3M")
phe_mult <- list(flowering_5 = c("FL50", "dyln_fl50", "cgdd_12c_gr2fl", "crain_gr2fl",
               "crain_1d"), greenup_2 = c("GR50", "cgdd_12c_10d"))
inputfiles <- read_delim(file.path(workingdir, "analysis", "gwas",
                                   "inputkinship.txt"),  delim = " ", 
                                   col_names = "SNPfiles")
```

```{r}
j=2
k=3
for(j in seq_along(phe_mult)){
  for(k in c(1,3)){
phe_suffix <- paste(phe_mult[[j]], subpop_v[k], 
                    sep = "*.*")
snp <- snp_attach(inputfiles$SNPfiles[k])
gwas_rds <- c()
for(i in seq_along(phe_suffix)){
gwas_rds1 <- pvdiv_results_in_folder(path = file.path(outputdir), 
                                      pattern = paste0("GWAS_datatable*.*",
                                                       phe_suffix[i]))
gwas_rds <- c(gwas_rds, gwas_rds1)
}
phenotypes_1 <- str_sub(gwas_rds, start = 16, end = -42) %>%
    str_replace(., "_$", "")

phenotypes <- paste0(names(subpop_v)[k], "_", phenotypes_1)
numSNPs <- round(ceiling(1200000/length(phenotypes)^2)/1000)*1000
out1phe <- pvdiv_bigsnp2mashr(path = file.path(outputdir), 
                           snp = snp, gwas_rds = gwas_rds, 
                           phenotypes = phenotypes, numSNPs = numSNPs, 
                           clump = TRUE, scaled = TRUE, saveoutput = TRUE,
                           suffix = paste0("single_phe_", names(subpop_v)[k], 
                                           "_", names(phe_mult)[j]))
  }
}
```

# Now make U_hyp in trait order. Try programmatically.
```{r}
library(rlist)
v <- matrix(data = 0, nrow=length(phenotypes), ncol=length(phenotypes))
v <- matrix(data = 0, nrow=16, ncol=16)

i=2 # site
j=2 # phe
k=1 # subpop: G&M, M, Gulf
suffix <- paste0("single_phe_", names(subpop_v)[k], "_", phe_mult[[j]][i])

m_single <- readRDS(file.path(outputdir, paste0("Strong_Effects1000SNPs_", 
                                                     suffix, ".rds")))

U_single <- m_single$fitted_g$Ulist[get_U_by_mass(m_single)]
names(m_single$fitted_g$Ulist)
U_s <- U_single[!names(U_single) %in% c("equal_effects", "identity", "simple_het_1", "simple_het_2", "simple_het_3")]

U_hyp <- list()

  for(q in seq_along(names(U_s))){
    s_length <- dim(U_s[[1]])[1]
    hyp1 <- v
    hyp1[c((i*s_length-s_length+1):(i*s_length)),c((i*s_length-s_length+1):(i*s_length))] <- U_s[[q]]
    U_hyp <- list.append(U_hyp, hyp1)
  }
q=1
j=1
U_single_list <- list()
for(j in seq_along(phe_mult)){
  suffix <- paste0("single_phe_", names(subpop_v)[k], "_", phe_mult[[j]][i])
  m_single <- readRDS(file.path(outputdir, paste0("Strong_Effects1000SNPs_", 
                                                  suffix, ".rds")))
  U_single1 <- m_single$fitted_g$Ulist[get_U_by_mass(m_single)]
  U_single_list <- list.append(U_single_list, U_single1)
}

for(n in )

gwas_rds1 <- pvdiv_results_in_folder(path = file.path(outputdir), 
                                      pattern = paste0("GWAS_datatable*.*",
                                                       phe_suffix[i]))
phenotypes_1 <- str_sub(gwas_rds1, start = 16, end = -42) %>%
    str_replace(., "_$", "")
```

```{r}
m_out <- mash_standard_run(path = outputdir, numSNPs = numSNPs, 
                           suffix = paste0(names(subpop_v)[k], 
                                           "_", names(phe_mult)[j]),
                           saveoutput = TRUE)
```

The trait order is the same order as the 'phenotypes' vector.
